---
title: "Plots"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <richard.wen@unityhealth.to>"
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  message=FALSE,
  warning=FALSE
)
options(readr.show_col_types = FALSE)
```

```{r, echo=FALSE, eval=FALSE}
#install.packages("tidyverse")
#install.packages("dplyr")
#install.packages("ggrepel")
#install.packages("patchwork")
```

# Libraries

```{r}
library(tidyverse)
library(dplyr)
library(ggrepel)
library(patchwork)
```

```{r, echo=FALSE}
cat("R Version\n---")
R.version

cat("\nPackage Versions\n---")
cat(paste0("\ntidyverse ", packageVersion("tidyverse")))
```

# Functions

## Metric Functions

Functions for PCCC and CSMF Accuracy.

```{r}

# Calc PCCC
calc_pccc <- function(actual, pred, k = 1, N = NULL, assume_zero = T) {
    
    # Calc N num of causes if not known
    N <- if (is.null(N)) length(unique(na.omit(c(actual, pred)))) else N
    
    # Calc frac of deaths in top k causes
    TP <- actual == pred
    TP[is.na(TP) | is.null(TP)] <- FALSE # for no preds
    C <- sum(TP) / length(actual)
    
    # Calc PCCC
    out <- (C - (k/N)) / (1 - (k/N))
    
    # Scale negative numbers to 0 for easier plotting
    out <- if (assume_zero & out < 0) 0 else out
    return(out)
}

# Calc CSMF accuracy
calc_csmf_acc <- function(actual, pred) {
    
    # Get all unique causes
    causes <- unique(c(actual, pred))
    
    # Get csmfs
    cases <- length(actual)
    csmf_true <- table(actual) / cases
    csmf_pred <- table(pred) / cases
    
    # Correct for missing causes in either actual or pred
    csmf_true <- vapply(
        causes,
        function(x) if (x %in% names(csmf_true)) csmf_true[x] else 0,
        FUN.VALUE = numeric(1)
    )
    csmf_pred <- vapply(
        causes,
        function(x) if (x %in% names(csmf_pred)) csmf_pred[x] else 0,
        FUN.VALUE = numeric(1)
    )
    
    # Calc csmf max error
    csmf_max_error <- 2 * (1 - min(csmf_true))
    
    # Calc csmf acc
    out <- 1 - (sum(abs(csmf_true - csmf_pred)) / csmf_max_error)
    return(out)
}
```

## Plot Functions

Functions for generating plots.

```{r}

# Plot performance of models
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2,
        text_mid_vjust = 2.5,
        text_end_size = 3,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 1.5,
        min_points_size = 2,
        max_points_size,
        x_limits = c(0, 1),
        ...
    ) {
    
    # Calc metric
    df_plot <- df_long %>%
        group_by(.data[[group]], model_name, .drop = F) %>%
        summarize( # calc pccc
            metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
        ) %>%
        mutate( # add pccc to model name
            model_label = paste0(model_name, " (", round(metric, 2), ")")
        )
    
    # Add min and max values for each cause of death
    df_ends <- df_plot %>%
        group_by(.data[[group]]) %>%
        summarize(
            min_metric = min(metric),
            max_metric = max(metric),
            model_min = model_name[which.min(metric)],
            model_max = model_name[which.max(metric)]
        ) %>%
        arrange(max_metric)
    
    # Sort cod by max model metric
    df_plot[[group]] <- factor(df_plot[[group]], levels = df_ends[[group]])
    df_ends[[group]] <- factor(df_ends[[group]], levels = df_ends[[group]])
    
    # Filter out the mid models
    df_mids <- df_plot %>%
        left_join(df_ends, by = group) %>%
        filter(model_name != model_max & model_name != model_min)
    
    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_point( # mid points
            data = df_mids,
            size = mid_points_size
        ) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, " (", round(min_metric, 2), ")")
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(model_max, " (", round(max_metric, 2), ")")
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_x_continuous(
            limits = x_limits,
            expand = expansion(add = 0.2)
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            panel.border = element_rect(
                color = "black",
                fill = NA,
                linewidth = 0.5
            ),
            legend.position = "none",
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank()
        )
    
    # Add min and max points
    if (add_min_points) {
        out <- out + geom_point( # min points
            data = df_ends,
            aes(x = min_metric),
            size = 2
        )
    }
    if (add_max_points) {
        out <- out + geom_point( # max points
            data = df_ends,
            aes(x = max_metric),
            size = 2
        )
    }
    return(out)
}

```

# Data

## Raw Data

Load data from `data` folder.

```{r}

# Read preds
df_raw <- read_csv("../data/healsl_rd1to2_cod_v1.csv")

# Display preds
cat("Cases: ", nrow(df_raw), "\n")
print(head(df_raw))

```

## Physician Cases

Filter for cases that were coded by physicians.

```{r}

# Filter for phy cases
df <- df_raw %>%
    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))

# Preview phy cases
cat("Non-coded Cases: ", nrow(df_raw) - nrow(df))
cat("\nPhysician Coded Cases: ", nrow(df))
df

```

## Combined Models

Create model combinations where if any of the models have the physician code, then set the combined model's output for the case to be the physician code. 

```{r}

# Calc combine preds
df <- df %>%
    mutate(
        "gpt3_insilicova_cghr10" = if_else(
            gpt3_cghr10 == physician_cghr10 | 
                insilicova_cghr10 == physician_cghr10,
            physician_cghr10,
            gpt3_cghr10
        ),
        "gpt4_insilicova_cghr10" = if_else(
            gpt4_cghr10 == physician_cghr10 | 
                insilicova_cghr10 == physician_cghr10,
            physician_cghr10,
            gpt4_cghr10
        ),
        "gpt3_interva5_cghr10" = if_else(
            gpt3_cghr10 == physician_cghr10 | 
                interva5_cghr10 == physician_cghr10,
            physician_cghr10,
            gpt3_cghr10
        ),
        "gpt4_interva5_cghr10" = if_else(
            gpt4_cghr10 == physician_cghr10 | 
                interva5_cghr10 == physician_cghr10,
            physician_cghr10,
            gpt4_cghr10
        ),
        "gpt3_insilicova_interva5_cghr10" = if_else(
            gpt3_cghr10 == physician_cghr10 | 
                insilicova_cghr10 == physician_cghr10 |
                interva5_cghr10 == physician_cghr10,
            physician_cghr10,
            gpt3_cghr10
        ),
        "gpt4_insilicova_interva5_cghr10" = if_else(
            gpt4_cghr10 == physician_cghr10 | 
                insilicova_cghr10 == physician_cghr10 |
                interva5_cghr10 == physician_cghr10,
            physician_cghr10,
            gpt4_cghr10
        )
    )

# Display combine preds
print(head(df %>% select(
    gpt3_insilicova_cghr10,
    gpt4_insilicova_cghr10,
    gpt3_interva5_cghr10,
    gpt4_interva5_cghr10,
    gpt3_insilicova_interva5_cghr10,
    gpt4_insilicova_interva5_cghr10
)))

```

## Inspect Data

Display case counts for raw data and prepared data after combining models and filtering for physician coded cases.

```{r}

cat("\nRaw Data\n--------\n\n")

# Physician info
raw_physicians <- df_raw$physician_cghr10
cat(paste0(
    "Cases (",
    length(unique(na.omit(raw_physicians))), " CODs): ",
    length(raw_physicians),
    "\n"
))

# Physician agreed cases
raw_physicians_agree <- df_raw %>%
    filter(is_agreed == TRUE) %>%
    pull(physician_cghr10)
cat(paste0(
    "Agreed Cases (",
    length(unique(na.omit(raw_physicians_agree))), " CODs): ",
    length(raw_physicians_agree),
    "\n"
))

# Models cases
raw_models <- df_raw %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(raw_models)) {
    m <- raw_models[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

cat("\nPrepared Data\n--------------\n")

# Physician cases
physicians <- df$physician_cghr10
cat(paste0(
    "Physician Coded Cases (",
    length(unique(na.omit(physicians))), " CODs): ",
    length(physicians) - sum(is.na(physicians) | is.null(physicians)),
    "\n"
))

# Physician agreed cases
physicians_agree <- df %>%
    filter(is_agreed == TRUE) %>%
    pull(physician_cghr10)
cat(paste0(
    "Physician Agreed Coded Cases (",
    length(unique(na.omit(physicians_agree))), " CODs): ",
    length(physicians_agree) - sum(is.na(physicians_agree) | is.null(physicians_agree)),
    "\n"
))

# Models cases
models <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models)) {
    m <- models[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

# Models agreed cases
models_agree <- df %>%
    filter(is_agreed == TRUE) %>%
    select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models_agree)) {
    m <- models_agree[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Agreed Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}
```

# Preparation

Prepare data for plotting.

## Agreed Cases

Filter for agreed cases only.

```{r}

# Agreed cases only
df <- df %>% filter(is_agreed == TRUE)

```

## Shorten COD Names

Shorten long names into new lines.

```{r}

# Shorten COD names
df <- df %>%
    mutate(physician_cghr10 = str_wrap(physician_cghr10, width = 34))

```

## Age Case Count

Count the number and percentage of cases for each age group.

```{r}
```

## COD Case Count

Count the number and percentage of cases for each CGHR-10 COD.

```{r}

# Count cases per cod
df <- df %>%
    left_join( # count cases and add as column
        df %>%
            group_by(age, physician_cghr10) %>%
            count(name = "physician_cghr10_n") %>%
            group_by(age) %>%
            mutate(
                physician_cghr10_perc = (physician_cghr10_n / sum(physician_cghr10_n)) * 100
            ),
        by = c("age", "physician_cghr10")
    )
df %>% select(rowid, age, physician_cghr10, physician_cghr10_n)
```

# Plots

Generate plots from the predictions.

```{r}

# Number of causes for each age group
ncod_adult <- 19
ncod_child <- 10
ncod_neo <- 7

# Model full name
gpt3_name <- "GPT-3.5"
gpt4_name <- "GPT-4"
isva_name <- "InSilicoVA"
iva5_name <- "InterVA-5"

# Pivot data into long format for calc
df_long <- df %>%
    filter( # remove low count cod
        physician_cghr10_n >= 10
    ) %>%
    pivot_longer( # long format
        ends_with("_cghr10") & !starts_with("physician_"),
        names_to = "model",
        values_to = "model_cghr10"
    ) %>%
    mutate(
        model = str_replace( # remove cghr10
            model,
            "_cghr10",
            ""
        ),
        model_name = str_replace_all(model, "_", " or ") %>% # use full model names
            str_replace(., "gpt3", gpt3_name) %>%
            str_replace(., "gpt4", gpt4_name) %>%
            str_replace(., "insilicova", isva_name) %>%
            str_replace(., "interva5", iva5_name),
        age_name = case_when( # use full age name
            age == "adult" ~ "Adult",
            age == "child" ~ "Child",
            age == "neo" ~ "Neonate",
            .default = NA
        ),
        cod = physician_cghr10,
        cod_name = paste0(
            cod,
            "\n(n=", physician_cghr10_n, ", ", round(physician_cghr10_perc), "%)"
        ),
        ncod = case_when( # num of cods for each age group
            age == "adult" ~ ncod_adult,
            age == "child" ~ ncod_child,
            age == "neo" ~ ncod_neo,
            .default = NA
        )
    ) %>%
    filter( # remove combine models
        !str_detect(model_name, " or ")
    )

# Calc num of records for each age
n_all <- df %>% group_by(age) %>% count
n_adult <- n_all %>% filter(age == "adult") %>% pull(n)
n_child <- n_all %>% filter(age == "child") %>% pull(n)
n_neo <- n_all %>% filter(age == "neo") %>% pull(n)

# Calc num of cods for each age
cod_all <- df_long %>% group_by(age) %>% summarize(n = n_distinct(cod))
cod_adult <- cod_all %>% filter(age == "adult") %>% pull(n)
cod_child <- cod_all %>% filter(age == "child") %>% pull(n)
cod_neo <- cod_all %>% filter(age == "neo") %>% pull(n)

# Preview
df_long

```

## PCCC By Age

```{r}
plot_perf(
    df_long,
    calc_pccc,
    group = "age_name",
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death",
    text_mid_size = 2.5,
    text_mid_vjust = 3
)
```

## PCCC by COD

Age, stage, cod.

```{r}

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("(a) Adult Records (n=", n_adult, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death"
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(b) Child Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) +
    plot_layout(
        heights = c(2, 1, 1),
        axis_titles = "collect"
    )

```

## CSMF Accuracy

Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model by age and physician coding stage.

```{r}

# Create csmf for each age group
csmf_adult <- list()
csmf_child <- list()
csmf_neo <- list()

```

## Plots

Save calculated metrics to `data` folder.

```{r}
out <- reduce(metrics,
              function(x, y) left_join(x, y, by = "Model")
)
write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
```

### Exploration

```{r}

# Num and perc of agreed cases
nall <- nrow(df)
nagree <- nrow(df %>% filter(is_agreed == TRUE))
pagree <- (nagree / nall) * 100

# Create labels to axis titles
y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")
```

#### Cases by Sex and Age Group

Display a plot of cases by age group separated by sex.

```{r}

# Calc age and sex counts
nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))

# Calc age and sex perc
padult <- (nadult / nagree) * 100
pchild <- (nchild / nagree) * 100
pneo <- (nneo / nagree) * 100

# Create age with counts
age_remap <- c(
    "Adult" = paste0("Adult, 12+ years\n(n=", nadult, ", ", round(padult), "%)"),
    "Child" = paste0("Child, 28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
    "Neo" = paste0("Neonatal, <28 days\n(n=", nneo, ", ", round(pneo), "%)")
)

# Format the data for plotting
asdata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(age, sex) %>%
    summarize(count = n()) %>%
    mutate(
        age = str_to_title(age),
        sex = paste0(
            sex, " (n=", count, ", ",
            round(count / case_when(
                age == "Adult" ~ nadult,
                age == "Child" ~ nchild,
                age == "Neo" ~ nneo
            ) * 100), "%)"
        )
    ) %>%
    mutate( # re-order age
        age = factor(age, levels = c(
            "Adult",
            "Child",
            "Neo"
        ))
    ) %>%
    mutate( # rename ages with counts
        age = recode(age, !!!age_remap)
    )

# Plot the data
asplot <- asdata %>%
    ggplot(aes(x = factor(age), y = count, fill = sex)) +
    geom_bar(
        stat = "identity",
        fill = "white",
        color = "black"
    ) +
    geom_text(
        aes(label = sex),
        position = position_stack(vjust = 0.5),
        size = 2.5,
        color = "black"
    ) +
    labs(
        y = y_title,
        x = element_blank(),
        fill = "Sex"
    ) +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10))
    )

# Save the plot
asplot
ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
```

#### Cases by Age Range

Display a plot for each age group of cases by age range.

```{r}
for (a in c("adult", "child", "neo")) {
    
    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
    
    # Format plot data
    eardata <- df %>%
        filter(is_agreed == TRUE & age == a) %>%
        group_by(age_range) %>%
        summarize(count = n()) %>%
        separate(
            age_range,
            into = c("age_range_value", "age_range_unit"),
            sep = " "
        ) %>%
        separate(
            age_range_value,
            into = c("age_range_min", "age_range_max"),
            sep = "-"
        ) %>%
        mutate(
            age_range_min = as.integer(age_range_min),
            age_range_max = as.integer(age_range_max),
            age_range_unit = factor(age_range_unit, levels = c(
                "Weeks",
                "Days",
                "Months",
                "Years"
            )),
            age_range_label = paste0(
                age_range_min,
                "-",
                age_range_max,
                " ",
                age_range_unit,
                "\n(n=", count, ", ", round((count / arows) * 100), "%)"
            )
        ) %>%
        arrange(age_range_unit, age_range_min, age_range_max) %>%
        mutate(
            age_range_label = factor(age_range_label, levels = unique(age_range_label))
        )
    
    # Plot the data
    earplot <- eardata %>%
        ggplot(aes(x = age_range_label, y = count)) +
        geom_bar(
            stat = "identity",
            fill = "#1d1d1d",
            color = "white",
            width = 0.5
        ) +
        labs(
            y = atitle,
            x = element_blank()
        ) +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10))
        ) +
        coord_flip()
    
    # Save the plot
    print(earplot)
    ggsave(
        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
        plot = earplot,
        dpi = 300
    )
}
```

#### Cases by COD

Display a plot for each age group of cases by cause of death.

```{r}
for (a in c("adult", "child", "neo")) {
    
    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
    
    # Format plot data
    ecoddata <- df %>%
        filter(is_agreed == TRUE & age == a) %>%
        group_by(physician_cghr10) %>%
        summarize(count = n()) %>%
        mutate(
            cod_label = paste0(
                if_else(
                    str_count(physician_cghr10, "\\s+") > 3,
                    str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
                    physician_cghr10
                ),
                "\n(n=", count, ", ",
                if_else(
                    ((count / arows) * 100) < 1,
                    "<1",
                    as.character(round((count / arows) * 100))
                ), "%)"
            )
        ) %>%
        arrange(count) %>%
        mutate(
            cod_label = factor(cod_label, levels = unique(cod_label))
        )
    
    # Plot the data
    ecodplot <- ecoddata %>%
        ggplot(aes(x = cod_label, y = count)) +
        geom_bar(
            stat = "identity",
            fill = "#1d1d1d",
            color = "white",
            width = 0.5
        ) +
        labs(
            y = atitle,
            x = element_blank()
        ) +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.text.x = element_text(hjust = 1)
        ) +
        coord_flip()
    
    # Save the plot
    print(ecodplot)
    ggsave(
        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
        plot = ecodplot,
        dpi = 300,
        width = if (a == "adult") 6 else NA,
        height = if (a == "adult") 8 else NA
    )
}
```

### Performance

#### All vs Agree Performance

Display a plot of model performance for all records versus records where physicians agreed on the COD code.

```{r, fig.height = 2.5, fig.width = 6}

# Calc stage counts
nall <- nrow(df)
nagree <- nrow(df %>% filter(is_agreed == TRUE))
nrecon <- nrow(df %>% filter(is_recon == TRUE))
nadj <- nrow(df %>% filter(is_adj == TRUE))

# Calc stage perc
pagree <- (nagree / nall) * 100
precon <- (nrecon / nall) * 100
padj <- (nadj / nall) * 100

# Create stage with counts
stage_remap <- c(
    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
    "Agreed" = paste0("Physician Agreed\nRecords\n(n=", nagree, ", ", round(pagree), "%)"),
    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
)

# Prepare boxplot data
alldata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`,
        `CSMF Accuracy`,
        `CSMF Accuracy Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy`,
            `CSMF Accuracy Agreement`
        ),
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    )

# Plot boxplot
allplot <- alldata %>%
    ggplot(aes(x = Stage, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_point(
        aes(y = `PCCC Mid Value`),
        shape = 1,
        size = 1.5,
        fill = "white",
        color = "darkgray",
        alpha = 0.8,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.055)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.055)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = element_blank(),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.85) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

# Save the plot
allplot
ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
```

#### Age Group Perfomance

Display a plot of performance for physician agreed records by age group.

```{r, fig.height = 3.5, fig.width = 6}

# Calc age counts
nagree <- nrow(df %>% filter(is_agreed == TRUE))
nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))

# Calc age perc
padult <- (nadult / nagree) * 100
pchild <- (nchild / nagree) * 100
pneo <- (nneo / nagree) * 100

# Create age with counts
age_remap <- c(
    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
)

# Prepare boxplot data
agedata <- out %>%
    select(
        Model,
        `PCCC Adult Agreement`,
        `PCCC Child Agreement`,
        `PCCC Neo Agreement`,
        `CSMF Accuracy Adult Agreement`,
        `CSMF Accuracy Child Agreement`,
        `CSMF Accuracy Neo Agreement`
    ) %>%
    rename(
         Adult = `PCCC Adult Agreement`,
         Child = `PCCC Child Agreement`,
         Neonatal = `PCCC Neo Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy Adult Agreement`,
            `CSMF Accuracy Child Agreement`,
            `CSMF Accuracy Neo Agreement`
        ),
        names_to = "Age Group",
        values_to = "PCCC"
    ) %>%
    group_by(`Age Group`) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(
                Model, "\n(", round(PCCC, 2),
                ", CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Mid Left" = if_else(
          `PCCC Mid Value` <= 0.5,
          `PCCC Mid`,
          NA
        ),
        "PCCC Mid Right" = if_else(
          `PCCC Mid Value` > 0.5,
          `PCCC Mid`,
          NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order age
        "Age Group" = factor(`Age Group`, levels = c(
            "Neonatal",
            "Child",
            "Adult"
        ))
    ) %>%
    mutate( # rename ages with counts
        "Age Group" = recode(`Age Group`, !!!age_remap)
    )

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_point(
        aes(y = `PCCC Mid Value`),
        shape = 1,
        size = 1.5,
        fill = "white",
        color = "darkgray",
        alpha = 0.8,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.055)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.055)
    ) +
    geom_text(
        aes(label = `PCCC Mid Left`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid Right`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.25, 0.9) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

# Save the plot
ageplot
ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
```

#### Sex Performance

Display a plot for each age group of performance for physician agreed records by sex.

```{r, fig.width = 6, fig.height = 2.5}
for (a in c("adult", "child", "neo")) {
    
    # Create label and ref for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
    aref <- str_to_title(a)
    
    # Get unique sex columns
    sex_col <- out %>% select(starts_with(sprintf(
            "PCCC %s Sex Agree ",
            aref
        ))) %>%
        names
    
    # Create sex with counts
    sex_remap <- list()
    sex_counts <- list()
    for (sx_col in sex_col) {
        
        # Get sex without prefix
        sx <- gsub(sprintf("PCCC %s Sex Agree ", aref), "", sx_col)
        
        # Calc num and perc cases for age range
        nsex <- df %>% filter(sex == sx & is_agreed == TRUE & age == a) %>% nrow
        psex <- (nsex / arows) * 100
        psex_label <- if (round(psex) >= 1) round(psex) else "<1"
        
        # Add label for age ranges
        sex_remap[[sx]] <- paste0(
            sprintf("%s %s", alabel, sx),
            "\n(n=", nsex, ", ", psex_label, "%)"
        )
        
        # Store age range count data
        sex_counts[[sx]] <- nsex
    }
    
    # Prepare boxplot data
    sxdata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Sex Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Sex Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Sex",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Sex" = recode(Sex, !!!sex_remap)
        ) %>%
        group_by(Sex) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Mid Value" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                PCCC,
                NA
            ),
            "PCCC Mid Left" = if_else(
                `PCCC Mid Value` <= 0.5,
                `PCCC Mid`,
                NA
            ),
            "PCCC Mid Right" = if_else(
                `PCCC Mid Value` > 0.5,
                `PCCC Mid`,
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )
    
    # Create cod order based on max pccc
    sxorder <- sxdata %>%
        group_by(Sex) %>%
        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
        select(Sex, `PCCC Max Value`) %>%
        arrange(desc(`PCCC Max Value`)) %>%
        pull(Sex)
    sxdata$Sex <- factor(sxdata$Sex, levels = rev(sxorder))
    
    # Plot boxplot
    sxplot <- sxdata %>%
        ggplot(aes(x = Sex, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_point(
            aes(y = `PCCC Mid Value`),
            shape = 1,
            size = 1.5,
            fill = "white",
            color = "darkgray",
            alpha = 0.8,
            position = position_nudge(x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.09)
        ) +
        geom_text(
            aes(label = `PCCC Mid Left`),
            color = "#4d4d4d",
            size = 2,
            hjust = 1,
            position = position_nudge(y = -0.025, x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Mid Right`),
            color = "#4d4d4d",
            size = 2,
            hjust = 0,
            position = position_nudge(y = 0.025, x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.09)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.04),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.04),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )
    
    # Save the plot
    print(sxplot)
    ggsave(
        sprintf("../manuscript/fig-perf-sex-%s.pdf", a),
        plot = sxplot,
        dpi = 300
    )
}
```

#### Detailed Age Range Performance

Display a plot for each age group of performance for physician agreed records by age ranges.

```{r}
for (a in c("adult", "child", "neo")) {
    
    # Create label and ref for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- if (a == "neo") {
        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
    } else {
        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
    }
    aref <- str_to_title(a)
    
    # Get unique age range columns
    arange_col <- out %>% select(starts_with(sprintf(
            "PCCC %s Age Agree ",
            aref
        ))) %>%
        names
    
    # Create age range with counts
    arange_remap <- list()
    arange_counts <- list()
    for (ar_col in arange_col) {
        
        # Get cod without prefix
        ar <- gsub(sprintf("PCCC %s Age Agree ", aref), "", ar_col)
        
        # Calc num and perc cases for age range
        narange <- df %>% filter(age_range == ar & is_agreed == TRUE & age == a) %>% nrow
        parange <- (narange / arows) * 100
        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
        
        # Add label for age ranges
        arange_remap[[ar]] <- paste0(
            ar,
            "\n(n=", narange, ", ", parange_label, "%)"
        )
        
        # Store age range count data
        arange_counts[[ar]] <- narange
    }
    
    # Prepare boxplot data
    ardata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Age Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Age Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Age Range",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Age Range" = recode(`Age Range`, !!!arange_remap)
        ) %>%
        group_by(`Age Range`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )
    
    # Create cod order based on max pccc
    arorder <- ardata %>%
        group_by(`Age Range`) %>%
        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
        select(`Age Range`, `PCCC Max Value`) %>%
        arrange(desc(`PCCC Max Value`)) %>%
        pull(`Age Range`)
    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(arorder))
    
    # Plot boxplot
    arplot <- ardata %>%
        ggplot(aes(x = `Age Range`, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.08)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.08)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.04),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.04),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )
    
    # Save the plot
    print(arplot)
    ggsave(
        sprintf("../manuscript/fig-perf-agerange-%s.pdf", a),
        plot = arplot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
    )
}
```

#### General Age Range Performance

Display a plot for each age group of performance for physician agreed records by age ranges.

```{r}
for (a in c("adult", "neo")) {
    
    # Create label and ref for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
    aref <- str_to_title(a)
    
    # Get unique age range columns
    arange_col <- out %>% select(starts_with(sprintf(
            "PCCC %s Age2 Agree ",
            aref
        ))) %>%
        names
    
    # Create age range with counts
    arange_remap <- list()
    arange_counts <- list()
    for (ar_col in arange_col) {
        
        # Get cod without prefix
        ar <- gsub(sprintf("PCCC %s Age2 Agree ", aref), "", ar_col)
        
        # Calc num and perc cases for age range
        narange <- df %>% filter(age_range2 == ar & is_agreed == TRUE & age == a) %>% nrow
        parange <- (narange / arows) * 100
        parange_label <- if (round(parange) >= 1) round(parange) else "<1"
        
        # Add label for age ranges
        arange_remap[[ar]] <- paste0(
            ar,
            "\n(n=", narange, ", ", parange_label, "%)"
        )
        
        # Store age range count data
        arange_counts[[ar]] <- narange
    }
    
    # Prepare boxplot data
    ar2data <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Age2 Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Age2 Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Age Range",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Age Range" = recode(`Age Range`, !!!arange_remap)
        ) %>%
        group_by(`Age Range`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )
    
    # Create cod order based on max pccc
    ar2order <- ar2data %>%
        group_by(`Age Range`) %>%
        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
        select(`Age Range`, `PCCC Max Value`) %>%
        arrange(desc(`PCCC Max Value`)) %>%
        pull(`Age Range`)
    ardata$`Age Range` <- factor(ardata$`Age Range`, levels = rev(ar2order))
    
    # Plot boxplot
    ar2plot <- ar2data %>%
        ggplot(aes(x = `Age Range`, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.08)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.08)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.04),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.04),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )
    
    # Save the plot
    print(ar2plot)
    ggsave(
        sprintf("../manuscript/fig-perf-agerange2-%s.pdf", a),
        plot = ar2plot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 3 else if (a == "neo") 2.5 else NA
    )
}
```

#### COD Performance

Plot model performance for physician agreed records by cause of death category.

Remove causes of death with less than 10 samples.

```{r}
for (a in c("adult", "child", "neo")) {
    
    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    aref <- str_to_title(a)
    
    # Create title for causes
    atitle <- paste0(
        "Physician Agreed ",
        alabel,
        " Records (n=", arows, ", 100%)"
    )
    
    # Get unique cause columns
    causes_col <- out %>% select(starts_with(sprintf(
        "PCCC %s COD Agree ", aref
    ))) %>% names
    
    # Create cod with counts
    cod_remap <- list()
    cod_counts <- list()
    for (cod_col in causes_col) {
        
        # Get cod without prefix
        cod <- gsub(sprintf("PCCC %s COD Agree ", aref), "", cod_col)
        
        # Calculate num and perc cases for cod
        ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE & age == a) %>% nrow
        pcod <- (ncod / arows) * 100
        pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
        
        # Break cod into newlines if more than 3 words
        if (str_count(cod, "\\s+") > 3) {
            cod_label <- str_replace(cod, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
        } else {
            cod_label <- cod
        }
        
        # Add label for cod
        cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
        
        # Store cod count data
        cod_counts[[cod]] <- ncod
    }
    
    # Get cods with less than 10 samples
    cod_low_counts <- cod_counts[cod_counts < 10]
    cod_low_perc <- sapply(cod_low_counts, function(x) {
        xprop <- (x / arows) * 100
        if (xprop < 1) {
            return("<1")
        } else {
            return(as.character(round(xprop)))
        }
    })
    cod_low_label <- paste0(
        names(cod_low_counts),
        " (n=", cod_low_counts, ", ", cod_low_perc, "%)",
        collapse = ", "
    )
    
    # Prepare boxplot data
    coddata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s COD Agree ", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s COD Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "COD",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "COD" = recode(`COD`, !!!cod_remap)
        ) %>%
        group_by(`COD`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        ) %>%
        filter( # remove CODs with <10 samples
            !str_detect(COD, paste0("^", names(cod_low_counts), collapse = "|"))
        )
    
    # Create cod order based on max pccc
    codorder <- coddata %>%
        group_by(COD) %>%
        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
        select(COD, `PCCC Max Value`) %>%
        arrange(desc(`PCCC Max Value`)) %>%
        pull(COD)
    coddata$COD <- factor(coddata$COD, levels = rev(codorder))
    
    # Plot boxplot
    codplot <- coddata %>%
        ggplot(aes(x = COD, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.12)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.12)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.06),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.06),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)",
            caption = if (length(cod_low_counts) > 0) paste0(
                length(causes_col) - length(cod_low_counts),
                " CODs shown / ",
                length(cod_low_counts),
                " CODs not shown (n<10): ",
                cod_low_label,
                "."
            ) else NULL
        ) +
        ylim(-0.3, 1.3) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            ),
            plot.caption = element_text(size = 7, face = "italic")
        )
    
    # Save the plot
    print(codplot)
    ggsave(
        sprintf("../manuscript/fig-perf-cod-%s.pdf", a),
        plot = codplot,
        dpi = 300,
        width = if (a == "adult") 8 else NA,
        height = if (a == "adult") 9 else NA
    )
}
```

#### COD Sensitivty and Specificity

Create heat map of sensitivity and specificity for each cause of death by model.

Remove causes of death with less than 10 samples.

```{r}
```
